### 2025-05-21 docs/article/Sections/state-of-the-art.tex
chapter 2 - Minor fix. Add link to Web tech survey. Simplify async/await description.

In traditional thread-per-request architectures, each incoming request is
handled by a dedicated thread. The web server maintains a thread pool from
which a thread is assigned to handle each request. As the load increases, the
number of active threads can grow rapidly, potentially exhausting the pool.
This can lead to performance and scalability issues, as the system may become
bogged down by context switching and thread management
overhead~\cite{kant2000scalable}. Spring MVC is one of the most widely used
frameworks that follows this model.

@@

Among mainstream technologies, the Kotlin programming language introduces a new 
abstraction for managing coroutines and provides structured concurrency, which 
ensures that coroutines are \textit{scoped}, \textit{cancellable}, and 
\textit{coordinated} within a well-defined 
lifecycle~\cite{elizarov2021coroutines}.
Although this model embraces the \texttt{async}/\texttt{await} 
feature~\cite{async_await}, enabling non-blocking routines to mimic the 
structure of synchronous ones and allowing developers to reason about control 
flow sequentially, it still lacks a user-level I/O subsystem and relies on an 
explicit I/O dispatcher tied to a dedicated thread pool that frees worker 
threads for handling processing tasks.
Moreover, web templates using their own templating dialects, such as JSP, 
Thymeleaf, or Handlebars, are unable to take advantage of such constructs, as 
they typically support only a limited subset of the host library's API—most 
commonly just the \texttt{Iterable} interface.

>>>>

In traditional thread-per-request architectures, each incoming request is
handled by a dedicated thread. The web server maintains a thread pool from
which a thread is assigned to handle each request. As the load increases, the
number of active threads can grow rapidly, potentially exhausting the pool.
This can lead to performance and scalability issues, as the system may become
bogged down by context switching and thread management
overhead~\cite{kant2000scalable}.
In the Java ecosystem, Spring Boot is one of the most widely used frameworks that
follow this model, according to several reports such as the Stack Overflow 2024
Developer
Survey~\footnote{~\url{https://survey.stackoverflow.co/2024/technology\#1-web-frameworks-and-technologies}}.

@@

Among mainstream technologies, the Kotlin programming language introduces a new 
abstraction for managing coroutines and provides structured concurrency, which 
ensures that coroutines are \textit{scoped}, \textit{cancellable}, and 
\textit{coordinated} within a well-defined 
lifecycle~\cite{elizarov2021coroutines}.
Although this model embraces the \texttt{async}/\texttt{await}
feature~\cite{async_await}, enabling non-blocking routines to mimic the
structure of synchronous ones, it still lacks a user-level I/O subsystem and
relies on an explicit I/O dispatcher tied to a dedicated thread pool that frees
worker threads for handling processing tasks.
Moreover, web templates using their own templating dialects, such as JSP, 
Thymeleaf, or Handlebars, are unable to take advantage of such constructs, as 
they typically support only a limited subset of the host library's API—most 
commonly just the \texttt{Iterable} interface.
